\thesisTitle

### 2019-10-09 proposal/paper.tex
a bit more on lta

\usepackage[						% use biblatex for bibliography
	backend=bibtex,					% 	- use biber backend (bibtex replacement) or bibtex
	style=numeric,					% 	- use alphabetic (or numeric) bib style
	natbib=true,					% 	- allow natbib commands
	hyperref=true,					% 	- activate hyperref support
	backref=true,					% 	- activate backrefs
	isbn=false,						% 	- don't show isbn tags
	url=false,						% 	- don't show url tags
	doi=false,						% 	- don't show doi tags
	urldate=long,					% 	- display type for dates
	maxnames=3,%
	minnames=1,%
	maxbibnames=5,%
	minbibnames=3,%
	maxcitenames=2,%
	mincitenames=1%
]{biblatex}
\bibliography{literature}

\usepackage[inline]{enumitem}

@@

Since not all data is well-suited for a fixed-dimensional vector representation, approaches that directly consider the structure of the input data might be more appropriate in such cases.
One such case is the class of so-called \textit{learning to aggregate} (LTA) problems as described by \citet{Melnikov2016}.
There the instances are represented by compositions $\bm{c}$ of constituents $c_i \in \bm{c}$, i.e.\@ variable-size multisets.
The assumption in LTA problems is that for all constituents $c_i$ a local valuation $y_i \in \mathcal{Y}$ is either given or computable.
The set of those local valuations should be indicative of the overall valuation $y \in \mathcal{Y}$ of the entire composition $\bm{c}$.
The goal of LTA is to learn a variadic aggregation function $A: \mathcal{Y}^{*} \to \mathcal{Y}$ that estimates such composite valuations, i.e.\@ $\hat{y} = A(y_1, \dots, y_n)$ for a composition with $n$ constituents.
Additionally the aggregation function $A$ should be associative and commutative to fit with the multiset-structure of compositions.

@@

Two main approaches to represent the aggregation function in LTA problems have been explored.
The first approach uses so-called uninorms~\cite{Melnikov2016} to do so.
There the basic idea is to express composite valuations as fuzzy logical assignments $y \in [0, 1]$.
Such a composite assignment $y$ is modeled as the result of a parameterized logical expression of constituent assignments $y_i \in [0, 1]$.
As the logical expression that thus effectively aggregates the constituents, a uninorm $U_{\lambda}$ is used.
Depending on the parameter $\lambda$, a uninorm interpolates between t-norms and t-conorms which correspond to logical conjunction and disjunction respectively.
\begin{align*}

\end{align*}

>>>>

\usepackage[						% use biblatex for bibliography
	backend=bibtex,					% 	- use biber backend (bibtex replacement) or bibtex
	style=numeric,					% 	- use alphabetic (or numeric) bib style
	natbib=true,					% 	- allow natbib commands
	hyperref=true,					% 	- activate hyperref support
	backref=true,					% 	- activate backrefs
	isbn=false,						% 	- don't show isbn tags
	url=false,						% 	- don't show url tags
	doi=false,						% 	- don't show doi tags
	urldate=long,					% 	- display type for dates
	maxnames=3,%
	minnames=1,%
	maxbibnames=5,%
	minbibnames=3,%
	maxcitenames=2,%
	mincitenames=1,%
	sorting=none
]{biblatex}
\bibliography{literature}

\usepackage[inline]{enumitem}
\usepackage{todonotes}

@@

Since not all data is well-suited for a fixed-dimensional vector representation, approaches that directly consider the structure of the input data might be more appropriate in such cases.
One such case is the class of so-called \textit{learning to aggregate} (LTA) problems as described by \citet{Melnikov2016}.
There the instances are represented by compositions $\bm{c}$ of constituents $c_i \in \bm{c}$, i.e.\@ variable-size multisets.
The assumption in LTA problems is that for all constituents $c_i$ a local score $y_i \in \mathcal{Y}$ is either given or computable.
The set of those local scores should be indicative of the overall score $y \in \mathcal{Y}$ of the entire composition $\bm{c}$.
The goal of LTA is to learn a variadic aggregation function $A: \mathcal{Y}^{*} \to \mathcal{Y}$ that estimates such composite scores, i.e.\@ $\hat{y} = A(y_1, \dots, y_n)$ for a composition with $n$ constituents.
Additionally the aggregation function $A$ should be associative and commutative to fit with the multiset-structure of compositions.

@@

Two main approaches to represent the aggregation function in LTA problems have been explored.
The first approach uses \textit{uninorms}~\cite{Melnikov2016} to do so.
There the basic idea is to express composite scores as fuzzy truth assignments $y \in [0, 1]$.
Such a composite assignment $y$ is modeled as the result of a parameterized logical expression of constituent assignments $y_i \in [0, 1]$.
As the logical expression that thus effectively aggregates the constituents, a uninorm $U_{\lambda}$ is used.
Depending on the parameter $\lambda$, $U_{\lambda}$ interpolates between t-norms and t-conorms which are continuous generalizations of logical conjunction and disjunction respectively.
\todo{TODO:\@ Details}

Recently \citet{Melnikov2019} have also looked at an alternative class of aggregation function.
Instead of using fuzzy logic to describe score aggregation, \textit{ordered weighted average} (OWA) operators were used.
\todo{TODO:\@ Details}
